\LARGE \bf A Semi-Automated Software Pipeline for Assembling Collision and Near-Collision Dashcam Footage Datasets

### 2021-04-10 paper.tex
rewrite methodology section to align with chen's comments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{METHODOLOGY}

Our pipeline is built from several modular components called executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor. Figure \ref{fig:pr_curve} illustrates the organization of the pipeline in its default configuration.

\begin{figure}[htbp]
	\centering
    \tikzset{
    	node distance = 6mm and 0cm,
        module/.style={%
            draw, rounded corners,
            minimum width=#1,
            minimum height=7mm,
            font=\sffamily
            },
        module/.default=1cm,
        >=LaTeX
    }
    \begin{tikzpicture}[
      % This will show the frame around the figure
      show background rectangle]

      % Place first 6 items
      \node[module] (crawler) {Web-Scrapers};
      \node[module, below=of crawler] (downloader) {Downloaders};
      \node[module, below=of downloader] (splitter) {Video-Splitter};
      \node[module, below=of splitter] (labeller) {Video-Labelling Tool};
      \node[module, below=of labeller] (uploader) {Data-Uploader};
      \draw[->] (crawler) -- (downloader);
      \draw[->] (downloader) -- (splitter);
      \draw[->] (splitter) -- (labeller);
      \draw[->] (labeller) -- (uploader);

    \end{tikzpicture}
		\caption{Architecture of the pipeline in its default configuration. Each node in the diagram represents a stage of the pipeline, consisting of a single executor or series of executors.}
		\label{fig:pipeline-architecture}
\end{figure}

\subsection{Video Collection}

The entry into our pipeline is a set of web scraper executors that each target and scrape a specific website or video repository based on a user-defined set of key-terms, and a \textit{database source executor} that pulls unlabelled videos from the user's database. Videos that are pulled by the scrapers are immediately added to the database with relevant metadata and marked as unlabelled. Subsequently, they are loaded into memory and sequentially fed into the pipeline. If the pipeline terminates before labelling a video, it remains flagged as unlabelled in the database and the video will be pulled in a subsequent run by the \textit{database source executor}. Crawler state is maintained via database lookup of specified key-value pairs to ensure duplicate data is not pulled. No video preprocessing such as resizing, trimming or cropping is automatically performed.

Users may define their own search terms to be used when querying the video repository. This value can be set in a YAML pipeline configuration file. By default, our scrapers query using the keywords: \texttt{Car crash dashcam}. Currently we support crawling Reddit and YouTube to locate videos that are of interest, and downloading videos hosted on YouTube and Imgur. Users that want to pull from a video repository that is not currently implemented should create a custom executor and implement the \texttt{iCrawler} interface. This new executor should be added as an entry point in a new YAML configuration and should generate and return a \texttt{MetaDataItem} with video source information to be used by a subsequent and corresponding downloader. \texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations. The \texttt{UniversalDownloader} then distributes \texttt{MetaDataItem} objects to their corresponding downloader by matching source URLs through regular expressions. New downloaders should be registered with the \texttt{UniversalDownloader} via a YAML pipeline configuration along with a regular expression string for URL matching.

@@

In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dashcam videos, and quick manual filtering of non-dashcam and irrelevant videos. Following Chan et al.\cite{chan2016anticipating}, if a collision occurs, we provide tools to annotate the frame where the collision occurs and bounding boxes to localize, identify and track agents in the video segment. Object tracking bounding boxes can be linearly interpolated from manual start and end points to improve ease of labelling. We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit variable download resolutions. For long-form videos that may contain multiple collision events or irrelevant video segments, such as compilation videos or videos with substantial editing and transitions, we provide a video clipping feature to demarcate the collision events from which we extract and generate distinct data points. 
Each video segment will eventually become a metadata item. Figure \ref{fig:example_gui_tool-png} shows an example of the GUI tool in usage.

\subsection{Metadata}
After all of the previous steps have been completed, the pipeline is able to produce a complete metadata object.
There are many fields in the metadata object (as can be seen in Figure \ref{metadata_example}):

\begin{itemize}
  %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
  \item "\texttt{description}": Description of the video as scraped from the video hosting website
  \item "\texttt{state}": String that describes the current labelling state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
  \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
  \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site- specific
  \item "\texttt{title}": The title of the video from the video hosting website
  \item "\texttt{url}": URL that the video was fetched from
  \item "\texttt{is\_split\_url}": Boolean that is true if the video has been segmented into multiple \texttt{MetaDataItem} objects during labelling, false otherwise
  \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
  \item "\texttt{start\_i}": The start frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
  \item "\texttt{end\_i}": The end frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
  \item "\texttt{bb\_fields}": All bounding-box specific data
  \begin{itemize}
    \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
    \item "\texttt{resolution}": List with 2 elements (width, height) representing the resolution in pixels of the video the bounding boxes were created for
    \item "\texttt{objects}": List of all of the relevant metadata pertaining to each agent in the video (either participant or bystander). Each item in this list includes the following:
    \begin{itemize}
      \item "\texttt{id}": Unique numerical identifier that represents this object
      \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a $1\times5$ array with elements in the following order: frame number, x1, y1, x2, y2
      \item "\texttt{class}": The class of the object (eg. "car", "pedestrian")
      \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
    \end{itemize}
  \end{itemize}
\end{itemize}

\begin{figure}[htbp]
  \begin{lstlisting}[language=json,xleftmargin=5mm]
{
  "description":"",
  "download_src":"YouTube",
  "tags": {
    "reddit_post_info":{
      "id":"<post_id>"
      "title":"title"
    }
  },
  "title":"Title of the Video",
  "url":"http://www.myvideo.com",
  "is_split_url": false,
  "enum_tags": ["NoCollision"],
  "start_i": 0,
  "end_i": 60,
  "bb_fields": {
    "collision_locations": [],
    "objects": [
      {
        "bboxes": [
          [0, 1096, 377, 1279, 634]
        ],
        "class": "car",
        "has_collision": false,
        "id": "1"
      }
    ],
    "resolution": [1280, 720]
  }
}
  \end{lstlisting}
    \caption{Example metadata produced by the pipeline}
    \label{metadata_example}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{AUTODASH 2021}
We aim to provide a dataset that contains a diverse set of egocentric vehicle collision videos with different locations and collision scenarios. In order to source these videos, we built a data pipeline that collects user-submitted videos from YouTube and Imgur. Using our pipeline, we collected and labelled 250 video clips of collision and near-collision scenarios from various locations in Europe, Asia, and North America. We have a variety of scene types such as city streets, highways, and rural areas from these locations. All video clips are annotated with bounding boxes for the vehicles and pedestrians present, as well as frame indices and object IDs for the participants in the collision.

\subsection{Video Collection Pipeline}
In order to facilitate collection of videos, we built a video discovery and annotation pipeline that can be customized for many labelling tasks. Our pipeline is built from several modular components called executors that each process or handle the data corresponding to a single video before piping the resulting data to the next executor using a pipe and filter architecture. The pipeline fetches and stores video metadata as JSON in a NoSQL cloud database and enables concurrent labelling of videos.

We collect a wide range of metadata on each video such as the set of bounding boxes for actors in the video, the object type of all the actors, the start frame of any collision in the video, and the location of the video.

The most basic pipeline configuration starts off with a set of web scrapers that each target and scrape a specific website or video repository based on a user-defined set of key-terms, and a \textit{database source executor} that pulls unlabelled videos from the  database. Videos that are pulled by the scrapers are immediately added to the database in order to ensure only one person is labeling a video at a time.

After a video has been downloaded to the user's machine, it is passed to the \textit{Splitter Executor}, which is used to split an input video into multiple sub-videos. We use the splitter for long-form videos that may contain multiple independent collision events or irrelevant video segments, such as compilation videos or videos with substantial editing and transitions. The \textit{Splitter} outputs a different metadata item for each distinct sub-video extracted from its input video.

After collection and preprocessing, a core component of our pipeline is a GUI tool (Figure \ref{fig:example_gui_tool-png}) that facilitates the manual annotation of the dashcam videos, and quick manual filtering of non-dashcam and irrelevant videos. We provide tools to annotate the video bounding boxes to localize, identify and track agents in the video segment, as well as ways to label the type of each agent and the location of the video. In order to assist with the manual labelling of bounding boxes, we provide ways to linearly interpolate between two user-drawn bounding boxes, so the user does not need to label every frame.

\subsection{Object Detection}
Every video in the dataset contians bounding boxes for all of the actors present in the video. Each actor is given a numerical ID, a list of bounding boxes that contain that actor for every frame they are present, as well as a classificaiton of the actor. There are 9 different classifications with the majority of objects being classified as one of "car", "truck", "van", or "motorcycle"

\subsection{Collision Detection}
Assisting in collision detection algorithms is the main purpose of this dataset, and as such we collect multiple pieces of data about the collision. We label and define a \textit{collision location} as the index of the first frame in the video for which at least one actor makes unintentional contact with another actor or stationary object. A given video may have multiple collision locations, especially in the case of highway scenes, and therefore each metadata contains a list of frame numbers for such events.

In addition to \textit{collision location} we classify every actor $a_i$ in the video with a \textit{has\_collision} flag that specifies if $a_i$ takes part in a collision at any point in the video.

% REMOVED IN REVISION
% Figure \ref{fig:pr_curve} illustrates the organization of the pipeline in its default configuration.

% \begin{figure}[htbp]
%     \centering
%     \tikzset{
%         node distance = 6mm and 0cm,
%         module/.style={%
%             draw, rounded corners,
%             minimum width=#1,
%             minimum height=7mm,
%             font=\sffamily
%             },
%         module/.default=1cm,
%         >=LaTeX
%     }
%     \begin{tikzpicture}[
%       % This will show the frame around the figure
%       show background rectangle]

%       % Place first 6 items
%       \node[module] (crawler) {Web-Scrapers};
%       \node[module, below=of crawler] (downloader) {Downloaders};
%       \node[module, below=of downloader] (splitter) {Video-Splitter};
%       \node[module, below=of splitter] (labeller) {Video-Labelling Tool};
%       \node[module, below=of labeller] (uploader) {Data-Uploader};
%       \draw[->] (crawler) -- (downloader);
%       \draw[->] (downloader) -- (splitter);
%       \draw[->] (splitter) -- (labeller);
%       \draw[->] (labeller) -- (uploader);

%     \end{tikzpicture}
%         \caption{Architecture of the pipeline in its default configuration. Each node in the diagram represents a stage of the pipeline, consisting of a single executor or series of executors.}
%         \label{fig:pipeline-architecture}
% \end{figure}

% Users may define their own search terms to be used when querying the video repository. This value can be set in a YAML pipeline configuration file. By default, our scrapers query using the keywords: \texttt{Car crash dashcam}. Currently we support crawling Reddit and YouTube to locate videos that are of interest, and downloading videos hosted on YouTube and Imgur. Users that want to pull from a video repository that is not currently implemented should create a custom executor and implement the \texttt{iCrawler} interface. This new executor should be added as an entry point in a new YAML configuration and should generate and return a \texttt{MetaDataItem} with video source information to be used by a subsequent and corresponding downloader. \texttt{MetaDataItem} objects are fed into the \texttt{UniversalDownloader} which aggregates \texttt{iDownloader} implementations. The \texttt{UniversalDownloader} then distributes \texttt{MetaDataItem} objects to their corresponding downloader by matching source URLs through regular expressions. New downloaders should be registered with the \texttt{UniversalDownloader} via a YAML pipeline configuration along with a regular expression string for URL matching.

@@

% In addition to collection and preprocessing, a core component of our pipeline is a GUI tool that facilitates the manual annotation of the dashcam videos, and quick manual filtering of non-dashcam and irrelevant videos. Following Chan et al.\cite{chan2016anticipating}, if a collision occurs, we provide tools to annotate the frame where the collision occurs and bounding boxes to localize, identify and track agents in the video segment. Object tracking bounding boxes can be linearly interpolated from manual start and end points to improve ease of labelling. We also save the video resolution at which the video was annotated to ensure bounding box annotations can always be scaled to fit variable download resolutions. 
% Each video segment will eventually become a metadata item. Figure \ref{fig:example_gui_tool-png} shows an example of the GUI tool in usage.

% \subsection{Metadata}
% After all of the previous steps have been completed, the pipeline is able to produce a complete metadata object.
% There are many fields in the metadata object (as can be seen in Figure \ref{metadata_example}):

% \begin{itemize}
%   %\item "collision\_type" contains the type of collision in the video (e.g. car vs. car)
%   \item "\texttt{description}": Description of the video as scraped from the video hosting website
%   \item "\texttt{state}": String that describes the current labelling state of the video. One of \textit{processed}, \textit{in-progress}, \textit{NULL}
%   \item "\texttt{download\_src}": The site that the video was sourced from (e.g. YouTube)
%   \item "\texttt{tags}": Object that contains custom user-defined tags on videos and additional data that is site- specific
%   \item "\texttt{title}": The title of the video from the video hosting website
%   \item "\texttt{url}": URL that the video was fetched from
%   \item "\texttt{is\_split\_url}": Boolean that is true if the video has been segmented into multiple \texttt{MetaDataItem} objects during labelling, false otherwise
%   \item "\texttt{enum\_tags}": List of tags identifying the content of the video. New tags can be added while labelling and can identify anything important in the video.
%   \item "\texttt{start\_i}": The start frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
%   \item "\texttt{end\_i}": The end frame of the video segment that the bounding boxes are created for (if \texttt{is\_split\_url} is true)
%   \item "\texttt{bb\_fields}": All bounding-box specific data
%   \begin{itemize}
%     \item "\texttt{collision\_locations}": List of frame numbers indicating the collision start frames
%     \item "\texttt{resolution}": List with 2 elements (width, height) representing the resolution in pixels of the video the bounding boxes were created for
%     \item "\texttt{objects}": List of all of the relevant metadata pertaining to each agent in the video (either participant or bystander). Each item in this list includes the following:
%     \begin{itemize}
%       \item "\texttt{id}": Unique numerical identifier that represents this object
%       \item "\texttt{bboxes}": List of bounding boxes for this specific object. Each bounding box is represented as a $1\times5$ array with elements in the following order: frame number, x1, y1, x2, y2
%       \item "\texttt{class}": The class of the object (eg. "car", "pedestrian")
%       \item "\texttt{has\_collision}": Boolean that is true if the object is in a collision, false otherwise
%     \end{itemize}
%   \end{itemize}
% \end{itemize}

% \begin{figure}[htbp]
%   \begin{lstlisting}[language=json,xleftmargin=5mm]
% {
%   "description":"",
%   "download_src":"YouTube",
%   "tags": {
%     "reddit_post_info":{
%       "id":"<post_id>"
%       "title":"title"
%     }
%   },
%   "title":"Title of the Video",
%   "url":"http://www.myvideo.com",
%   "is_split_url": false,
%   "enum_tags": ["NoCollision"],
%   "start_i": 0,
%   "end_i": 60,
%   "bb_fields": {
%     "collision_locations": [],
%     "objects": [
%       {
%         "bboxes": [
%           [0, 1096, 377, 1279, 634]
%         ],
%         "class": "car",
%         "has_collision": false,
%         "id": "1"
%       }
%     ],
%     "resolution": [1280, 720]
%   }
% }
%   \end{lstlisting}
%     \caption{Example metadata produced by the pipeline}
%     \label{metadata_example}
% \end{figure}
